Limited information strategies for topological games

### 2015-03-10 phd/talks-and-presentations/2015-03-11-defense.tex
final draft of defense slides

>>>>

\begin{frame}{
Proof that $\sigma$-compact $\Leftrightarrow$ $\pl F\markwin\menGame{X}$
}\small
  Assume $X$ is regular.

  If $X=\bigcup_{n<\omega} K_n$, then $\pl F$ may choose $K_n$ each round,
  which is a winning predetermined (and therefore Markov) strategy.

  If $X$ is not $\sigma$-compact,
  let $\sigma$ be any Markov strategy for $\pl F$. Then for
    \[
      R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \sigma(\<\mc{U}\>,n)
    \]
  and any open cover $\mc U$ of the space $X$,
  $\sigma(\<\mc{U}\>,n)$ is a finite subcover of $R_n$. Thus $\cl{R_n}$
  is compact by the regularity of $X$.

  Since $X$ is not $\sigma$-compact, choose a point $x$ not in any $R_n$.
  Then there is a sequence of open covers $\mc U_0,\mc U_1,\dots$ for which
  $x\not\in\sigma(\<\mc U_n\>,n)$ for all $n$, and thus $\sigma$
  is not a winning Markov strategy.
\end{frame}

\begin{frame}{
Proof that $\pl F\win\menGame{X}$ $\Leftrightarrow$ $\pl F\markwin\menGame{X}$
}\small
  Assume $X$ is second-countable. Without loss of generality, assume
  $\pl C$ only chooses coverings using open sets from the countable base
  $\{U_n:n<\omega\}$.

  If $\pl F$ has a winning Markov strategy, then she has a winning strategy.

  Let $\sigma$ be a winning strategy, and assume $\mc U_t$ is an open cover
  of basic open sets for each $t\leq s\in\omega^{<\omega}$.
  % Since $\sigma(\<\mc U_{s\rest1},\dots,\mc U_{s},\mc U\>)$
  % is finitely coverable by $\mc U$,
  % there is some $F\in[\omega]^{<\omega}$ such that
  % $
  %   \sigma(\<\mc U_{s\rest1},\dots,\mc U_{s},\mc U\>)
  %     \subseteq
  %   \bigcup_{n\in F}U_n
  % $.
  % Since there are only countably many $F\in[\omega]^{<\omega}$,
  By exploiting the countable base, we may choose
  $\mc U_{s\concat\<n\>}$ for each $n<\omega$, such that for every open cover
  $\mc U$ there exists $n<\omega$ where
  $
    \sigma(\<\mc U_{s\rest1},\dots,\mc U_{s},\mc U\>)
      \subseteq
    \sigma(\<\mc U_{s\rest1},\dots,\mc U_{s},\mc U_{s\concat\<n\>}\>)
  $.

  Then
  $\tau(\<\mc U\>,n)=\sigma(\<\mc U_{f(n)\rest1},\dots,\mc U_{f(n)},\mc U\>$
  where $f:\omega\to\omega^{<\omega}$ is a bijection is a winning strategy.
\end{frame}
